---
title: "Tidyverse Recipe - Police Killings"
author: "Chester Poon"
date: "11/26/2018"
output:
  prettydoc::html_pretty:
    theme: cayman
---

#Tidyverse Recipes for Police Killings in 2015.

I'll be using the data behind police killings in 2015, which is available here:
<https://github.com/fivethirtyeight/data/tree/master/police-killings>

I'm actually using this same dataset for my Data 606 project, so a far deeper analysis is to come.

###Loading the data

First, we'll load just some of the data and then using dplyr's `select` function, well just take some of the variables that we want.

```{r, message=FALSE, warning=FALSE}
library(tidyverse)

# load data - We'll pull just some of the variables we want.
pd_killing <- read.csv('police_killings.csv')
pd_killing <- select(pd_killing,name,
                     raceethnicity,
                     tract_ce,
                     armed,
                     pop,
                     share_white,
                     share_black,
                     share_hispanic,
                     h_income
                     )
```

###Cleaning some of the data

There are variables described as the share of the population in a certain census tract. For example, if the value is 50 for `share_white`, then this actually means that 50% of the population in that census tract is white. It would probably be more appropriate to convert these to the correct value of 0.5. The below code accomplishes this.

```{r, message=FALSE, warning=FALSE}
#Convert share to numeric proportion
pd_killing$share_white <- 
  as.numeric(levels(pd_killing$share_white))[as.integer(pd_killing$share_white)]/100
pd_killing$share_black <- 
  as.numeric(levels(pd_killing$share_black))[as.integer(pd_killing$share_black)]/100
pd_killing$share_hispanic <- 
  as.numeric(levels(pd_killing$share_hispanic))[as.integer(pd_killing$share_hispanic)]/100
pd_killing$tract_ce <- as.factor(pd_killing$tract_ce)
```

###Subset our data

Now that our data is generally clean, we can subset our data into a new data frame. I've left some room in `pd_ksub` for others to contribute where appropriate. `pd_killing` will also be preserved to leave some room for others to contribute as well.

```{r, message=FALSE, warning=FALSE}
#Subset and prepare the data.
pd_ksub <- pd_killing %>%
  filter(armed == 'No',
         raceethnicity %in% c('White','Black')) %>%
  select(raceethnicity,
         pop,
         tract_ce,
         share_white,
         share_black)

knitr::kable(head(pd_ksub), format = "html")
```

